%Here be dragons...


This dissertation concludes the findings of my master project \emph{Deep Learning for Counterfactual Inference} at the University of Oxford. I am taking this opportunity to express my sincere gratitude to all the people who helped me along the way and ultimately made this possible.

Firstly, I would like to thank my supervisor Prof. Dr. Mihaela van der Schaar for her guidance and for showing me an exciting problem to work on. In addition, I was fortunate to be working with her PhD student Ahmed Alaa who provided valuable feedback and fresh ideas whenever I was struggling. 

Furthermore, I would like to acknowledge my secondary supervisor Prof. Dr. Edith Elkind, my departmental supervisor Dr. Milos Nikolic, and  my academic advisor Dr. Garrett Morris of Green Templeton College for their guidance throughout this year. 

A master's program can be challenging on many levels. Therefore, I am grateful for the community and encouragements I received from the inhabitants of 39 St. Margaret's Road and my friends from the department and Green Templeton College who made this year such an unforgettable experience. 

Most of all, I would like to thank my father Jenö, my mother Ingrid, my sister Elisabeth, and my girlfriend Albana for their unfailing support  --- day-and-night even in the most stressful situations. 

I would not have been able to do it without you. 

\begin{flushright}
Michael 
\end{flushright}

%This is where you thank your advisor, colleagues, and family and friends.

% Supervisor: Mihaela + Ahmed
% My friends 
% Rosi und Papa
% Lisi
% Albana

